%-------------------------
% Author : Nikolay Kudinov
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfencoding=auto,
}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Nikolay Kudinov} \\
  \vspace{1pt}
  Berlin, Germany \\
  \href{mailto:nikolay.a.kudinov@gmail.com}{\underline{nikolay.a.kudinov@gmail.com}} \\
  Phone: +49 15123317890
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Results-driven backend engineer specializing in distributed systems, microservices, and high-performance architectures. Proficient in scalable cloud solutions (AWS, Kubernetes) and fault-tolerant applications. Experienced in database performance tuning and query optimization, improving efficiency and reliability. Passionate about solving large-scale engineering challenges and system design.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading{Senior Software Engineer}{05/2021 -- Present}{Zalando}{Berlin, Germany}
    \resumeItemListStart
      \resumeItem{Designed and implemented an innovative suspicious activity detection system based on address
      similarity, capable of detecting 97\% of similar addresses, significantly improving genuie customers
      purchase success rates for popular items.}
      \resumeItem{Engineered an emergency onboarding process for hyped articles, capable of handling more than 10K+ events/min using Flink, DynamoDB, ensuring high availability and fault tolerance during peak demand, and stabilizing critical systems across Zalando.}
      \resumeItem{Optimized backend algorithms to improve the turnover of limited-stock items, resulting in increased sales performance.}
      \resumeItem{Communicated effectively and closely collaborated with other teams during the collection requirement phase for GhostAds, leading efforts to ensure cross-functional alignment.}
      \resumeItem{Optimized the Ad Campaign Management endpoints, reducing response latency by 40\% and enhancing system throughput, significantly improving the Ads platform's responsiveness under high-load conditions.}    
    \resumeItemListEnd

    \resumeSubheading{Senior Software Engineer – Java \& Scala}{09/2014 -- 04/2021}{Deutsche Bank}{Germany}
    \resumeItemListStart
      \resumeItem{Developed and optimized Job Manager, a system for tracking trade processing job statuses, enhancing monitoring and efficiency.}
      \resumeItem{Reduced Input Data Cache (IDC) startup time by 60\%, improving data availability for a 15K-node calculation grid that supports trade, market, and reference data.}
      \resumeItem{Optimized CVA risk calculations, reducing processing time from 24 hours to 4 hours, enabling multiple intra-day recalculations and enhancing business agility.}
      \resumeItem{Developed multiple data collectors to gather trade and risk data, supporting FRTB (Fundamental Review of the Trading Book) compliance by ensuring accurate capital calculations under Basel III regulations.}
    \resumeItemListEnd

    \resumeSubheading{Senior Software Engineer}{10/2012 -- 08/2014}{Rostelecom}{Russia}
    \resumeItemListStart
      \resumeItem{Developed multiple extensions for the General Ledger module, improving functionality and integration within the financial system.}
      \resumeItem{Proactively optimized system performance, enhancing overall efficiency with a focus on salary calculation processes, the most critical system component, through advanced SQL tuning and query optimization.}
    \resumeItemListEnd

    \resumeSubheading{Software Engineer}{11/2006 -- 10/2012}{Luxoft (Dell Dedicated Center)}{Russia}
    \resumeItemListStart
      \resumeItem{Developed an Order Rejection System, streamlining error detection for the support team and improving issue resolution during order processing.}
      \resumeItem{Led the development of an interface to efficiently load orders into the core backend system, enhancing order processing workflows.}
      \resumeItem{Spearheaded a global data invoice and order migration project for 16 APAC business units, ensuring seamless data transition and system integration.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------LEADERSHIP-----------
\section{Leadership}
  \resumeSubHeadingListStart
     \resumeItemListStart
       \resumeItem{Moderator for the DDIA \& System Design Telegram community, comprising 1,400+ job seekers and industry mentors. Actively involved in moderating online events focused on discussing and analyzing research papers related to distributed systems.}
       \resumeItem{Founder of the largest Apache Spark Telegram community. Organized and hosted 10+ online meetups in 2020, focusing on Apache Spark internals. Delivered presentations, available at: \href{https://github.com/nkudinov/apache\_spark\_pptx}{\texttt{apache\_spark\_pptx}}.}
     \resumeItemListEnd
  \resumeSubHeadingListEnd


  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{Moscow Aviation Institute (National Research University)}{}{Master’s Degree, Applied Mathematics}{}
  \resumeSubHeadingListEnd

%-----------SKILLS & CERTIFICATIONS-----------
  \section{Skills, Licenses, and Certifications}  
  \resumeItemListStart  
    \resumeItem{\textbf{Programming Languages:} Java, Scala, SQL, PL/SQL, Python}  
    \resumeItem{\textbf{Databases \& Storage:} Oracle, PostgreSQL, ClickHouse, DynamoDB, Redis}  
    \resumeItem{\textbf{Distributed Systems \& Data Processing:} Apache Spark, Flink,  Akka Streams, Alpakka, Apache Kafka}  
    \resumeItem{\textbf{Backend \& Cloud Infrastructure:} Spring Boot, Kubernetes, Grafana, OpenTelemetry, AWS (IAM, S3, DynamoDB)}  
    \resumeItem{\textbf{Performance Optimization:} Advanced SQL tuning, query optimization, database internals, and high-throughput system design}  
    \resumeItem{\textbf{Certifications:} Oracle Certified Professional, Java SE 8 Programmer, Functional Programming Principles in Scala}
    \resumeItem{\textbf{System Design \& Architecture:} Scalability, Microservices, Fault-Tolerance, High Availability}  
    \resumeItem{\textbf{Data Structures \& Algorithms:} Strong problem-solving skills, 1100+ Leetcode problems solved} 
  \resumeItemListEnd  
%-------------------------------------------
\end{document}
